---
title: "drpr-vignette"
author: "Neil Diamond"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{drpr-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

#Introduction

An R package, drpr, has been built to undertake the DRP calculations in R.

```{r, echo=FALSE}
library(printr)
```

To install the package you use the command "install.packages('drpr_0.992.zip', repos=NULL)". 

  
You then need to load the package:
```{r, echo=TRUE, eval==TRUE}
library("drpr")

Jan15m <- Jan15[order(Jan15$Maturity),][-1,]

```

Note that Jan15 is an example data file. In the following, I have used Jan15 with the bond with the lowest maturity removed. The user can load his or her own data using say "Dec15 <- read.csv('Dec15.csv')" where the .csv file must have (at least) three numeric columns labelled "Maturity", "Yield",
and "Amount.issued".

#No Adjustment for Credit Raings
  
##Gaussian Smoothing

The underlying Gaussian smoothing is done by the gswt1() function. For convenience, the gkest1() calls the gswt1() function for target terms to maturity of 3, 5, 7, and 10 years. The documentation for the two functions and an Example is given below:

```{r, echo=TRUE}
?gswt1
?gkest1
fit0 <- gswt1(data=Jan15m)
print(fit0)
summary(fit0)
```

```{r, echo=T, fig.height=6,fig.width=8}
plot(fit0)
```

```{r}
```




##Fitting the Nelson-Siegel model

The Nelson-Siegel model is fitted using the fitnelsonsiegel() function. Be default, the starting value for the decay factor is 0.7173, which is the value maximising the loading of the curvature factor for a maturity of 2.5 years.

```{r, echo=TRUE}
library(drpr)
library(minpack.lm)
?fitnelsonsiegel
fitnelsonsiegel(Jan15m)
```



```{r, echo=TRUE}
fit1 <- fitnelsonsiegel(Jan15m)
print(fit1)
summary(fit1)
```

```{r, echo=T, fig.height=6,fig.width=8}
plot(fit1)
```

```{r}
```


##Fitting the Nelson-Siegel-Svensson model

The Nelson-Siegel-Svensson model is fitted using the fitnelsonsiegelsvensson() function. Be default, the starting value for the two decay factors maximise the loading of the curvature factor for a maturity of 2.5 years and a maturity of 5 years. However, note well, the inverse decay factors are used.


```{r, echo=TRUE}
?fitnelsonsiegelsvensson
fitnelsonsiegelsvensson(Jan15, lambda1start=1/lambdastart(2.5),
                               lambda2start=1/lambdastart(5))
```


```{r, echo=TRUE}
fit2 <- fitnelsonsiegelsvensson(Jan15m, lambda1start=1/lambdastart(2.5),
                               lambda2start=1/lambdastart(5))
print(fit2)
summary(fit2)
```

```{r, echo=T, fig.height=6,fig.width=8}
plot(fit2)

```

###Fixing the lambda parameters
If the lambda parameters are fixed then they can be input with the option fixed=T.

```{r}
fit2a <- fitnelsonsiegelsvensson(Jan15, lambda1start=0.17,
                               lambda2start=3.4038, fixed=T)
print(fit2a)
summary(fit2a)
```


##Obtaining the DRP

The average of the annualised ten year yield estimates using the three estimation techniques are combined with the average spot rate to give an annualised DRP. At this stage it is required to input the average spot rate on a semi-annual basis.

```{r, echo=TRUE}
?drp
drp(fit0, fit1, fit2, avspotratesa=2.9546)
```


##Comparisons

The package can be used to make graphical comparisons between the three techniques:

```{r, echo=TRUE, fig.height=6,fig.width=8}
drpplot(fit0, fit1, fit2)
```

```{r}
```


#Adjusting for Credit Raings

A major shortcoming of the calculations above is that they do not adjust for credit ratings. Additional functions are provided that do this adjustment.

##Gaussian Smoothing

The function gswt1adjust() adjusts for credit ratings using the technique of backfitting. This is an iterative technique: First the credit ratings are ignored and the usual Gaussian Kernel is applied. Then a linear model is fitted to the residuals and the fitted model is used to adjust for the credit ratings. The process is continued until convergence. In most case only a small number of iterations are required.

```{r, echo=TRUE}
?gswt1adjust
?gkest1adjust
fit3 <- gswt1adjust(data=Jan15m)
```




```{r, echo=TRUE, fig.height=6,fig.width=8}
print(fit3)
summary(fit3)
```

```{r, echo=T, fig.height=6,fig.width=8}
plot(fit3)
```

```{r}
```


##Fitting the Nelson-Siegel model

The model allows the level parameter to depend on the credit rating but the other parameters are constrained to be the same. 

```{r, echo=TRUE}
library(drpr)
library(minpack.lm)
?fitnelsonsiegeladjust
fit4 <- fitnelsonsiegeladjust(Jan15m)
```


```{r, echo=TRUE}
print(fit4)
summary(fit4)
```

```{r, echo=T, fig.height=6,fig.width=8}
plot(fit4)
```

```{r}
```


##Fitting the Nelson-Siegel-Svensson model

The model allows the level parameter to depend on the credit rating but the other parameters are constrained to be the same.

```{r, echo=TRUE}
?fitnelsonsiegelsvenssonadjust
fit5 <- fitnelsonsiegelsvenssonadjust(Jan15m, lambda1start=1/lambdastart(2.5),
                               lambda2start=1/lambdastart(5))
```


```{r, echo=TRUE}
print(fit5)
summary(fit5)
```

```{r, echo=T, fig.height=6,fig.width=8}
plot(fit5)
```

```{r}
```



##Obtaining the DRP

The three results are combined.

```{r, echo=TRUE}
?drpadjust
drpadjust(fit3,fit4,fit5, avspotratesa=2.9546)
```

#The code

```{r, echo=TRUE}
gswt1
gkest1
getS3method("print", "GaussianSmooth")
getS3method("summary", "GaussianSmooth")
getS3method("plot", "GaussianSmooth")
lambdastart
fitnelsonsiegel
getS3method("print", "NelsonSiegel")
getS3method("summary", "NelsonSiegel")
getS3method("plot", "NelsonSiegel")
fitnelsonsiegelsvensson
getS3method("print", "NelsonSiegelSvensson")
getS3method("summary", "NelsonSiegelSvensson")
getS3method("plot", "NelsonSiegelSvensson")
drp
drpplot
gswt1adjust
gkest1adjust
getS3method("print", "GaussianSmoothAdjust")
getS3method("summary", "GaussianSmoothAdjust")
getS3method("plot", "GaussianSmoothAdjust")
fitnelsonsiegeladjust
getS3method("print", "NelsonSiegelAdjust")
getS3method("summary", "NelsonSiegelAdjust")
getS3method("plot", "NelsonSiegelAdjust")
fitnelsonsiegelsvenssonadjust
getS3method("print", "NelsonSiegelSvenssonAdjust")
getS3method("summary", "NelsonSiegelSvenssonAdjust")
getS3method("plot", "NelsonSiegelSvenssonAdjust")
drpadjust
```

#Example Data

```{r, echo=TRUE, size=fit1}
Jan15[,c(4,7,10,11)]
```

